\documentclass[a4paper, 11pt]{article}
\usepackage{geometry}
\geometry{letterpaper, margin=1in}
\usepackage{graphicx}
\graphicspath{ {images/} }

\usepackage{amsmath}
\usepackage{amssymb}  
\usepackage{amsthm}
\usepackage{ulem}

\usepackage{enumitem}


\usepackage{pdfpages} % for including full pdf pages

\usepackage{empheq}

\usepackage{listings}


%format to allow bolded theorems, corollaries, etc...
\newtheorem*{theorem}{Theorem}
\newtheorem*{corollary}{Corollary}
\newtheorem*{lemma}{Lemma}
\newtheorem*{definition}{Definition}
\newtheorem*{Example}{Example} 
\newtheorem*{Remark}{Remark}

% stop typing \mathbb a thousand times 
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\F}{\mathbb{F}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\sphere}{\mathbb{S}}

% commands for bra-ket notation
\newcommand{\bra}[1]{\ensuremath{\left\langle#1\right|}}
\newcommand{\ket}[1]{\ensuremath{\left|#1\right\rangle}}
\newcommand{\bracket}[2]{\ensuremath{\left\langle #1 \middle| #2 \right\rangle}}
\newcommand{\matrixel}[3]{\ensuremath{\left\langle #1 \middle| #2 \middle| #3 \right\rangle}}
\newcommand{\expectation}[1]{\ensuremath{\left\langle #1 \right\rangle}}

% vector stuff
\newcommand{\basis}[1]{\hat{\mathbf{e}}_#1}
\newcommand{\unit}[1]{\hat{\boldsymbol{#1}}}
\newcommand{\bvec}[1]{\vec{\boldsymbol{#1}}}


% change margins for solution
\newenvironment{solution}{%
	\begin{list}{}{%
			\setlength{\topsep}{0pt}%
			\setlength{\leftmargin}{0.5cm}%
			\setlength{\rightmargin}{0.5cm}%
			\setlength{\listparindent}{\parindent}%
			\setlength{\itemindent}{\parindent}%
			\setlength{\parsep}{\parskip}%
		}%
		\item[]}{\end{list}}



\begin{document}
\noindent
\large\textbf{Class Notes} \hfill \textbf{John Waczak} \\
\normalsize CS 162 \hfill  Date: \today 
\par\noindent\rule{\textwidth}{0.4pt} \\\\


% \begin{lstlisting}[language=C++]
% \end{lstlisting}

\section*{Objects \& Structures}
Objects are a way to think about grouping together similar items in order to
organize their structure and inter-relations. In programming, objects are a way
to group variables together (as in arrays). \textit{Arrays} allow us to group
together objects so long as they are the same type.

\begin{lstlisting}[language=C++]
  int grades[150]; 
\end{lstlisting}
But what if we want more flexibility? We need to move away from the
\textit{primitive} variable types and begin to group different variables
together in order to make a sort of container.\\ 

\textbf{Structs} are custom objects (structures) that allow us to mix and match
data types. Traditionally, structures contain only data and no member functions
i.e. a clump of related variables. The following shows an example. \\


\begin{lstlisting}[language=C++]
  struct book{
    int pages;
    unsigned in pub_date;
    string title; // a string inside the struct
    int num_authors;
    string* authors; // a pointer to a string
  };

  // declare a book struct
  book text_book; 
\end{lstlisting}
\vspace{1em}

Inside of \textit{book} we have defined a number of useful variables such as a
string for the title, an int for the number of pages, etc... How do we access
these?


\begin{lstlisting}[language=C++]
  book bookshelf[10];
  for (int i = 0; i < 10; i++){
    bookshelf[i].num_pages = 100;
    bookshelf[i].title = ``Place holder''
    bookshelf[i].authors = new string[2]; // dynamically allocate array 
  }
\end{lstlisting}


\section*{Pointers}
\begin{itemize}
\item Pointers $==$ memory addresses.
  
\item Variable declaration creates a variable on the stack

\begin{lstlisting}[language=C++]
int a = 5;
\end{lstlisting}
  
\item Pointer declaration
  
\begin{lstlisting}[language=C++]
int* b = &a; 
\end{lstlisting}
This creates a pointer variable of type \textbf{int} which points to the address
of \textbf{a} (using the address operator \&)

\item Dereferencing a pointer:
  
\begin{lstlisting}[language=C++]
cout << *b << endl; 
\end{lstlisting}
This will take the pointer b and grab the variable held at that memory location. 

\end{itemize}



\section*{Array}
\begin{itemize}
  \item An \textit{array} is a collection variables of one data type and its
    memory is stored contiguously

  \item \textit{static arrays} are created on the stack and are of a fixed size

\begin{lstlisting}[language=C++]
int stack_array[10]; 
\end{lstlisting}
    
  \item \textit{Dynamic arrays} are created on the heap and their size may
    change during runtime.

    
\begin{lstlisting}[language=C++]
int *heap_array = new int[10]; 
\end{lstlisting}

  \item Arrays can be of one ore more dimensions

    
\begin{lstlisting}[language=C++]
int stack_array_2d[5][7]; 
\end{lstlisting}
\end{itemize}




% \begin{lstlisting}[language=C++]
% \end{lstlisting}
\section*{Makefiles}
The compilation process is deceptively complicated. It must find pre-processor
directives and expand macros. It has to compile the code and translate it into
assembly. Then it has to run the assembler and translate to machine code.
Finally it has to run the linker and translate the files into an executable. \\

\noindent Using a makefile allows us to stop the compilation at any point and break the
process into manageable chunks. \\

\noindent The basic structure of the makefile is

\begin{lstlisting}[language=C++]
<target>: dependencies
    shell commands
\end{lstlisting}
Any time any of the dependencies change or are updated, the target is rerun.  

\begin{lstlisting}[language=C++]
clean:
    rm -r *.out *.o 
\end{lstlisting}
The clean target is used to remove all generated files so that you can rebuild
from scratch. 


\begin{lstlisting}[language=C++]
.PHONY
\end{lstlisting}
This target allows you to create a list of files and file types for make to
ignore. \\


\section*{Memory Leaks}
To detect memory leaks, use the command line tool \textit{valgrind}. At the end,
valgrind gives you a summary of memory lost with a particular category for
definitely lost and indirectly lost. Valgrind will not tell you however where
the memory leak is. \\

To try and find this, we can use the $-g$ flag on compile to use debugging. We
can do this in our makefile! $-Wall$ will display all warnings. 


\begin{lstlisting}[language=C++]
DEBUG ?= 1
ifeq ($(DEBUG), 1)
    CFLAGS := -g -Wall
else 
    CFLAGS := -DNDEBUG -03
endif
\end{lstlisting}
now we can add a $\$(CFLAGS)$ 

\end{document}

































