\documentclass[a4paper, 11pt]{article}
\usepackage{geometry}
\geometry{letterpaper, margin=1in}
\usepackage{amsmath}
\usepackage{amssymb}  
\usepackage{amsthm}
\usepackage{ulem} 
\usepackage{graphicx}
\usepackage{enumitem} % use for making lettered list 
\usepackage{bbm} % use for making the 1 identity operator EX: \mathbbm{1}
\usepackage{subfig} 
\graphicspath{ {images/} }

% format to allow bolded theorems, corollaries, etc... 
\newtheorem*{theorem}{Theorem}
\newtheorem*{corollary}{Corollary}
\newtheorem*{lemma}{Lemma}
\newtheorem*{definition}{Definition}
\newtheorem*{Example}{Example} 
\newtheorem*{Remark}{Remark}

% stop typing \mathbb a thousand times 
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\F}{\mathbb{F}}
\newcommand{\Mat}[2]{\mathcal{M}_{#1\times#2}}

% change margins for solution
\newenvironment{solution}{%
	\begin{list}{}{%
			\setlength{\topsep}{0pt}%
			\setlength{\leftmargin}{1.5cm}%
			\setlength{\rightmargin}{1.5cm}%
			\setlength{\listparindent}{\parindent}%
			\setlength{\itemindent}{\parindent}%
			\setlength{\parsep}{\parskip}%
		}%
		\item[]}{\end{list}}

\begin{document}
%Header-Make sure you update this information!!!!
\noindent
\large\textbf{Class notes} \hfill \textbf{John Waczak} \\
\normalsize MTH 443 \hfill  Last Updated: \today \\
Dr. Schmidt
\par\noindent\rule{\textwidth}{0.4pt}	
	
\section*{Notation Comments} 
	\begin{Remark}
		The notation $L_A:\F^n \to F^m$ when $A\in M_n(\F)$ has the letter $L$ to indicate left multiplication by A on column vectors. 
	\end{Remark}

	\begin{Remark}
		Given any linear operator $T:V\to V$, and finite ordered bases $B, C$ for $V$. The matrix of $T$ with respect to $B$ and $C$ is denoted $[T]_B^C$. In particular, 
			\begin{equation}
				[Id_v]_C^B = \Big([Id_v]_b^C\Big)^{-1}
			\end{equation}
		From this, 
			\begin{align}
				[T]_C^C &= [Id_v]_B^C\; [T]_B^B\; [Id_v]_C^B \\ 
					&= Q^{-1}\;[T]_B^C\; Q
			\end{align}
		where $Q = [Id_v]_C^B$ is the change of basis matrix. 
	\end{Remark}

\section*{Cosets}
	If U is a subspace of V and $v\in V$ then the left coset of U in V represented by v is
		\begin{equation}
			v+U = \{v+u|u\in U\}
		\end{equation}
	The \textbf{set of left cosets} of U in V is 
		\begin{equation}
			V/U = \{v+U | v \in V\}
		\end{equation}
	Note that if $v\in V$ and $u \in U$ then $v+U = (v+u)+U$. Naively, we could hope that 
		\begin{align*}
			V/U \times V/U &\to V/U  \\ 
			(v_1+U, v_2+U) &\mapsto (v_1+v_2)+U
		\end{align*}
	actually defines a function. We have to be sure that when you choose some $v_1', v_2'$ that the resulting coset is the same... i.e. that we need to check that this really is a function for which inputs have exactly one output. That is, 
		\begin{align*}
			(v_1+U, v_2+U) \mapsto v_1+v_2+U
		\end{align*}
	is well-defined, in the sense that the right hand side value is independent of choice of coset representatives of the initial cosets. Here, if $v_1' = v_1+u_1$, $v_2' = v_2+u_2$ with $u_i \in U$. Now 
		\begin{equation*}
			v_1' + v_2' + U = \Big[(v_1+u_1)+(v_2+u_2)\Big]+ U
		\end{equation*}
	Thus,
		\begin{align*}
			v_1'+v_2'+U &= (v_1+u_1+v_2) + (u_2 + U) \\ 
				&= (v_1+v_2+u_1) + U \\ 
				&= v_1+v_2 + U
		\end{align*}
	That is, since addition on V is Abelian, every subgroup U is normal and thus the naive formula does give a well-defined function. We now check if 
		\begin{align*}
			\F \times V/U &\to V/U \\ 
			(\lambda, v+U)&\mapsto \lambda v + U
		\end{align*}
	is a well-defined function (\textbf{IT IS}). So the family of cosets of subspace U in vector space V is itself a vector space over $\F$. 
	
	\begin{lemma}
		Suppose U is a vector subspace of V, and B is a basis of U. Let $C = B\cup B'$ be any basis of V extending B. Then, $\{v+U | v \in B'\}$ is a basis of our quotient vector space $V/U$. 
	\end{lemma}
	\begin{proof}
		Suppose $\sum_i \lambda_i (v_i+U) = 0_{V/U}$ for some $\lambda_1,..., \lambda_n \in \F$. and $v_1, ... , v_n \in B'$. Since $0_{V/U} = 0_v + U = U$ is our zero vector, thus
			\begin{align*}
				\Big(\sum_i^n \lambda_i v_i\Big) + U = U
			\end{align*} 
		This holds if and only if 
			\begin{align*}
				\sum_i^n \lambda_i v_i \in U
			\end{align*}
		However, the $v_i\in B'$ and hence are linearly independent of the $sp(B)$. Therefore, this linear combination can only be $0_V\in U$. But $C$ is a basis and thus all of the $\lambda_i=0$. Note if $U=V$ then $V/U$ is only $\{0_v + U\}$ and one uses logical statements. 
	\end{proof}

\section*{More on cosets}
	\noindent Recall that given $U$ is a subspace of $V$, we let $V/U$ be the quotient vector space, whose elements are cosets, thus of the form $v+U = \{ v+u|u\in U \}$. We call $v$ a coset representative of $v+U$; in general, cosets have many representative. We checked that 
		\begin{align*}
			V/U \times V/U &\to V/U \\ 
			(v_1+U, v_2+U)&\mapsto (v_1+v_2)+U\\
			\F \times V/U &\to V/U \\ 
			(\lambda, v+U)&\mapsto \lambda v+U
		\end{align*}
	are functions. (We needed to check that their values were independent of coset representatives). You check that $V/U$ is then an $\F$-vectorspace.  \\ 
	
	\noindent Recall further that if $B$ is a basis for $U$ and $B'$ is such that $C=B\cup B'$ is a basis of $V$ extending $B$, then $\{v+U | v\in B'\}$ is a basis for $V/U$. 
	
	
	\begin{lemma}
		Let $U$ be a subspace of $V$ and define 
			\begin{align*}
				\pi:V&\to V/U \\ 
				v &\mapsto v+U
			\end{align*}
		Then $\pi$ is a surjective linear transformation whose kernel is $U$. 
	\end{lemma} 
	\begin{proof}[sketch]
		We check linearity:
		\begin{align*}
			\pi(\lambda v_1+v_2) &= (\lambda v_1 + v_2)+ U \\ 
				&= (\lambda v_1 + U) + (v_2 + U) \\ 
				&= \lambda(v_1+U)+(v_2+U) \\ 
				&= \lambda\pi(v_1)+\pi(v_2) 
		\end{align*}
		$\forall \lambda \in \F$, $\forall v_1, v_2 \in V$. Thus the function $\pi$ is a linear transformation. Surjectivity is clear. Now we check the kernel. If $v\in \ker(\pi)$, then $\pi(v) = 0_{V/U} = 0_v+U$ that is $v+U = U$. Hence $v \in U$. The "other direction" holds equally well; $\ker(\pi) = U$. 
	\end{proof}

	\begin{lemma}
		If $T:V\to W$ is a linear transformation, let $\bar{T}:V/\ker(T)\to W$ be given by
			\begin{equation*}
				\bar{T}(v+\ker(T)) = T(v)
			\end{equation*}
		$\forall v \in V$. Then, $\bar{T}$ is a linear transformation, which is injective. 
	\end{lemma}
	\begin{proof}
		We must first check that $\bar{T}$ is a well-defined function. Suppose $v_1, v_2\in V$ are such that $v_1 + \ker(T) = v_2 + \ker(T)$. In particular, this means 
			\begin{align*}
				v_1 - v_2 \in \ker(T)
			\end{align*} 
		Hence $T(v_1 - v_2) = 0_W$. By the linearity of T, $T(v_1)-T(v_2) = 0_w$; that is $T(v_1)=T(v_2)$. Thus $\bar{T}$ is well-defined. Now $\forall \lambda \in \F$, $v_1, v_2 \in V$, 
			\begin{align*}
				\bar{T}(\lambda (v_1+ \ker(T)) + (v_2+\ker(T))) &= \bar{T}(\lambda v_1 + v_2+\ker(T)) \\ 
				&= T(\lambda v_1 + v_2) \\ 
				&= \lambda T(v_1) + T(v_2) \\ 
				&= \lambda\bar{T}(v_1+\ker(T)) + \bar{T}(v_2+\ker(T))
			\end{align*}
		Thus, $\bar{T}$ is a linear transformation. Recall any linear transformation is injective if and only if its kernel is trivial ($\{0_V\}$). \\ 
		
		\noindent Suppose $\bar{T}(v + \ker(T)) = 0_W$. Then $T(v) = 0_W$. Hence $v\in\ker(T)$. Thus, $v+\ker(T) = \ker(T) = 0_{V/U}$. Therefore, $\bar{T}$ is injective
	\end{proof}
	
	
	\begin{corollary}
		Given a linear transformation $T:V\to W$, we have $V/\ker(T) \text{ iso } T(V)$
	\end{corollary} 
	\begin{proof}
		By the lemma, $\bar{T}:V/\ker(V)\to W$ is injective. Its range, $R_T = \{ T_v | v\in V\}$ Certainly, any linear transformation 
	\end{proof}
\end{document}






























