\documentclass[a4paper, 11pt]{article}
\usepackage{geometry}
\geometry{letterpaper, margin=1in}
\usepackage{amsmath}
\usepackage{amssymb}  
\usepackage{amsthm}
\usepackage{ulem} 
\usepackage{graphicx}
\usepackage{physics}
\graphicspath{ {images/} }

\begin{document}
%Header-Make sure you update this information!!!!
\noindent
\large\textbf{Assignment 4 Reflection} \hfill \textbf{John Waczak} \\
\normalsize CS 161 \hfill  Date: \today \\

\subsection*{Understanding}
	\paragraph{}
	I think that having had the experience of trying to write the almost-tic-tac-toe game last week, these tasks were much more straight forward and easy to implement. Mostly, I attribute this to the fact that we weren't allowed to submit a main file and therefore the problem descriptions were much more verbose. For example, it was quite easy to follow the requirements for the ship and bboard classes.  
	
\subsection*{Testing Plan}
	\paragraph{}
	I believe that my testing plan was helpful. Once again though, it was difficult to test our classes and I ultimately just ended up running the test cases I had planned as well as a test or two for every function I defined in my implementation files. Hopefully I interpreted the assignment correctly but that is difficult to comment on without having received a grade yet. 

\subsection*{Design}
	\paragraph{}
	The design for both parts of the assignment was very simple to write as the problems outlined what was required in pretty clear detail. There were only a few things that required some careful thinking such as how to tell if a ship has been sunk. One of the challenges was refraining from defining unnecessary extraneous variables that the problem did not ask for. 
\subsection*{Implementation} 
	\paragraph{}
	I had some trouble implementing the pointers for both tasks mostly just due to small syntax errors like accidentally using (*) instead of (\&) and visa versa for constructing, getting the reference of a variable, and dereferencing the variable. .  Other than that I think the clear assignment plan as well as problem descriptions made it quite easy to get started writing. I did not have any major difficulties or setbacks. 
\subsection*{Improvement} 
	\paragraph{} 
	To improve my code I think it would be nice to add more member functions that could be useful for writing a game program. For example, creating a function for a turn of the game would be easy and likely would have to implement everything previously written. 
	

		
\end{document}